Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Massive cleanup

  \item
  \S\ref{frontend} details other concerns, such as distributed state management and extensibility.
\end{itemize}

\noindent
\sys's implementation~\sx{impl} evaluation~\sx{eval} show significant speedups on both parallel and distributed execution, using a combination of micro-bench\-marks---popular shell one-liners that highlight certain features---and multi-line macro-benchmarks---a web crawling and indexing engine, a genomics pipeline, and a popular weather analysis script.
After a comparison with related prior work~\sx{related}, the paper closes with a discussion of related work and possible future directions~\sx{discussion}.
% \bigskip
% \begin{quote}
% \footnotesize
Additional material, in anonymized form, is available at
\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
% \end{quote}

@@

In order to address this, we have designed a categorization language
that is flexible enough to identify commands to different categories
given their options. The complete language syntax can be seen in
\Cref{fig:dsl}.

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
\todo{The DSL attempts to capture important elements regarding the distributability aspects of various commands.}
\vspace{-15pt}
}

@@

We assume that the arguments of a command can always be separated to
options and file arguments (checking if they start with a
\ttt{-}~\footnote{Note that the single character \ttt{-} is not an
  option as it is most often used to designate that a command reads
  from its standard input}). A file written in the language contains a
record containing a mapping from predicates to assignments for each
command. Predicates can be simple boolean formulas on the existence
and the value of all options. Each assignment contains the command
category, the sequence of its input sources, and its output
source. Inputs to commands are a sequence of file arguments and its
standard input. Similarly, the output is either its standard output or
a file argument. An example record for comm can be seen below:

@@

As mentioned in distributability, pure commands can be broken down
into different categories. We might be able to get ideas about this
from this paper:
\url{http://www.cs.toronto.edu/~azadeh/papers/pldi17-ex.pdf} and its
continuation in PLDI 2019.

\tr{Can we find a solution for the commands in coreutils?}

@@

\section{Front End}
\label{frontend}

\kk{The writing in this section is wandering around without a clear
  purpose :( }

\kk{It might make sense to merge this section with the one below with
  the name: From Shell to IR and back}

@@

\section{Implementation}
\label{impl}
\kk{I think that this section should be merged with the front end}

\paragraph{Dish Optimizer}

@@

\kk{Maybe give an example}

@@

\subsection{Just in time planning}

\TODO{Rename this section to planner activators and write it after I
  discuss with Nikos.}

\kk{This whole section for just in itme planning, is also relevant for
  the front end. If the front end is executed just in time, it would
  have more information, and maybe it could make a sound analysis.}

@@

\TODO{Niko, could you make this a bit stronger?}

@@

\kk{We should make sure to measure the time that it takes for the
  whole process to run (parsing, translating, optimizing, planning)
  together with the scripts. This will probably be negligible, but we
  still have to mention it. }

\kk{Also, we have to have one-two handcrafted examples that have more
  than one pipeline, to show the execution time end to end, as this
  cannot be shown with the one-pipeline examples since they only have
  one graph, so no back and forth between shell and dish.}

\kk{Furthermore it would be great to have one distributed example that
  runs in more than one node (if we have time)}

\kk{Also we have to make sure to measure with and without the final
  cat of output file, so that we show that this is also negligible.}

\kk{We have to make sure that we repeat that the results are the same
  in all tests that we run. Corectness, blah blah ...}

\kk{We should have at least some pipelines that have a bad pure
  command in them.}

@@

>>>>

  \item
  \S\ref{impl} details other concerns, such as distributed state management and extensibility.
\end{itemize}

\noindent
\sys's evaluation~\sx{eval} shows significant speedups on both parallel and distributed execution, using a combination of micro-bench\-marks---popular shell one-liners that highlight certain features---and multi-line macro-benchmarks---a web crawling and indexing engine, a genomics pipeline, and a popular weather analysis script.
After a comparison with related prior work~\sx{related}, the paper closes with a discussion of related work and possible future directions~\sx{discussion}.
% \bigskip
% \begin{quote}
% \footnotesize
Additional material, in anonymized form, is available at
\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
% \end{quote}

@@

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
\todo{The DSL attempts to capture important elements regarding the distributability aspects of various commands.}
\vspace{-20pt}
}

@@

\heading{Distributability DSL}
\sys's distributability description DSL (Fig.~\ref{fig:dsl}) is designed to be able to classify a commands into multiple categories given their options.

It assumes that the arguments of a command can always be separated to
options and file arguments (checking if they start with a
\ttt{-}~\footnote{Note that the single character \ttt{-} is not an
  option as it is most often used to designate that a command reads
  from its standard input}). A file written in the language contains a
record containing a mapping from predicates to assignments for each
command. Predicates can be simple boolean formulas on the existence
and the value of all options. Each assignment contains the command
category, the sequence of its input sources, and its output
source. Inputs to commands are a sequence of file arguments and its
standard input. Similarly, the output is either its standard output or
a file argument. An example record for comm can be seen below:

@@

% As mentioned in distributability, pure commands can be broken down
% into different categories. We might be able to get ideas about this
% from this paper:
% \url{http://www.cs.toronto.edu/~azadeh/papers/pldi17-ex.pdf} and its
% continuation in PLDI 2019.
% FIXME: \nv{Cite this paper?}
\tr{Can we find a solution for the commands in coreutils?}

@@

\section{Implementation}
\label{impl}
% \kk{The writing in this section is wandering around without a clear
%   purpose :( }
% 
% \kk{It might make sense to merge this section with the one below with
%   the name: From Shell to IR and back}

@@

\subsection{Dish Optimizer}

@@

\nv{Give example, extend}

@@

\subsection{Planning Activators and Just-in-Time Planning}

\nv{Nikos working on this and next}

% \kk{This whole section for just in itme planning, is also relevant for
%   the front end. If the front end is executed just in time, it would
%   have more information, and maybe it could make a sound analysis.}

@@

@@

% FIXME
% \kk{We should make sure to measure the time that it takes for the
%   whole process to run (parsing, translating, optimizing, planning)
%   together with the scripts. This will probably be negligible, but we
%   still have to mention it. }
% 
% \kk{Also, we have to have one-two handcrafted examples that have more
%   than one pipeline, to show the execution time end to end, as this
%   cannot be shown with the one-pipeline examples since they only have
%   one graph, so no back and forth between shell and dish.}
% 
% \kk{Furthermore it would be great to have one distributed example that
%   runs in more than one node (if we have time)}
% 
% \kk{Also we have to make sure to measure with and without the final
%   cat of output file, so that we show that this is also negligible.}
% 
% \kk{We have to make sure that we repeat that the results are the same
%   in all tests that we run. Corectness, blah blah ...}
% 
% \kk{We should have at least some pipelines that have a bad pure
%   command in them.}

@@

\subsection{Microbenchmarks: Shell One-liners}

\subsection{Macro-benchmark: Weather Analysis}

\subsection{Macro-benchmark: Web Crawling}

\subsection{Macro-benchmark: Bioinformatics Transform}
